### 2021-10-13 content/80.formal-definition.tex
Footnote URLs. Cite RDF 1.1

The $Root(r)$ is a type of $Dataset(r)$, and must have the metadata to literal attributes to provide a $name$, $description$ and $datePublished$, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 requirements for the root data entity\footnote{
    \href{https://www.researchobject.org/ro-crate/1.1/root-data-entity.html\#direct-properties-of-the-root-data-entity}
}.

The concept of an $Entity(e)$ is introduced as being either a $DataEntity(e)$, a $ContextualEntity(e)$, or both\footnote{
    \href{https://www.researchobject.org/ro-crate/1.1/contextual-entities.html\#contextual-vs-data-entities}
}; and must be typed with at least one $Class(e)$.

@@

A formalized RO-Crate in $\mathcal{L}_{rocrate}$ can be mapped to different serializations.
Assume a simplified\footnote{
 This simplification does not cover the extensive list of literal datatypes built-in to RDF 1.1, only strings and decimal real numbers. Likewise, language of literals are not included.
} language $\mathcal{L}_{RDF}$
based on the \href{http://www.w3.org/TR/2014/REC-rdf11-concepts-20140225/}{RDF abstract syntax}:

>>>>

The $Root(r)$ is a type of $Dataset(r)$, and must have the metadata to literal attributes to provide a $name$, $description$ and $datePublished$, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 requirements for the root data entity\footnote{
    \url{https://www.researchobject.org/ro-crate/1.1/root-data-entity.html\#direct-properties-of-the-root-data-entity}
}.

The concept of an $Entity(e)$ is introduced as being either a $DataEntity(e)$, a $ContextualEntity(e)$, or both\footnote{
    \url{https://www.researchobject.org/ro-crate/1.1/contextual-entities.html\#contextual-vs-data-entities}
}; and must be typed with at least one $Class(e)$.

@@

A formalized RO-Crate in $\mathcal{L}_{rocrate}$ can be mapped to different serializations.
Assume a simplified\footnote{
 This simplification does not cover the extensive list of literal datatypes built-in to RDF 1.1, only strings and decimal real numbers. Likewise, language of literals are not included.
} language $\mathcal{L}_{RDF}$
based on the RDF abstract syntax \cite{rdfworkinggroup_2014}:
